\documentclass{ximera}
      
\title{Confidence Intervals}
      
\begin{document}
      
\begin{abstract}
      
In this activity, we examine the $Z$. Confidence Interval.

\url{https://cnx.org/contents/MBiUQmmY@18.54:H9wp31Fq@9/A-Single-Population-Mean-using}

      
\end{abstract}
      
\maketitle
 

\begin{onlineOnly}
$$\graph[xmin=-2,xmax=2,ymin=-0.5,ymax=1, panel]{N=e^{-x^2/2}/(2\pi)^{(0.5)}, P=\int_{z_1}^{z_2} N dx, a=-1, b=1, s=1, m=0, z_1=(a-m)/s, z_2=(b-m)/s, 0<y<N\left\{z_1<x<z_2\right\}}$$
\end{onlineOnly}
(This graph allows one to visualize and compute normally distributed probabilities.  Sliders $a$ and $b$ control the left and right endpoints, whereas $m, s$ denote the mean and standard deviation respectively.  Then $P$ is proportion of the normal curve between $a$ and $b$ with $z$-scores $z_1, z_2$ respectively.  A larger version of this graph may be found here: \url{https://www.desmos.com/calculator/y1pdds9uga}.)


\begin{sageCell}
from scipy.stats import norm

normdist = norm()

mean=120 # Put the mean of the distribution here
std=30  # Put the standard deviation of the distribution here.
P=0.4  # P is the value such that everything to the left of X is P

X=normdist.ppf(P)*std+mean

print('The area to the left of '+`X`); print(' on the normal curve with mean '+`mean`); print(' and standard deviation '+`std`); print(' is  '+`P`)
\end{sageCell}
(The above SageCell allows one to input a probability/area $P$ and it will find a value $X$ so that the probability/are to the \textbf{LEFT} of $X$ is $P$.)


Round to 4 decimal places iff necessary.


\begin{problem}
Health care workers NW who use latex gloves with glove powder on a daily basis are particularly susceptible to developing a latex allergy. Symptoms of a latex allergy include conjunctivitis, hand eczema, nasal congestion, a skin rash, and shortness of breath. A sample of 46 hospital employees who were diagnosed with latex allergy based on a skin-prick test reported on their exposure to latex gloves (Current Allergy & Clinical Immunology, March 2004). Summary statistics for the number of latex gloves used per week are $\bar{x} = 19.3$ and $\sigma = 11.9.$

\begin{enumerate}
\item Find a 95\% confidence interval for this data.  $[\answer{15.8611},\answer{22.7389}]$
\item At least how many employees should be sampled to achieve a 99\% confidence interval with 2 glove error? $\answer{278}$
\end{enumerate}

\end{problem}



\begin{problem}
Refer to the American Secondary Education (Fall 2009) study of middle school students? usage of laptop computers. Recall that for a sample of 106 students, the researchers reported the following statistics on how many minutes per day each student used a laptop for taking notes: $\bar{x} = 13.2$, $\sigma = 19.5$. Now the researchers want to estimate the average amount of time per day laptops are used for taking notes for all middle school students across the country.
\begin{enumerate}
\item Find a 90\% confidence interval for the average number of time students spend on laptops per day taking notes. $[\answer{10.0846}, \answer{16.3154}]$
\item At least how many students should be sampled for there to be a achieve a 99\% confidence interval with a 12 second error? $\answer{61987}$
\end{enumerate}


\end{problem}








\end{document}
