\documentclass{ximera}
      
\title{Counting}
      
\begin{document}
      
\begin{abstract}
      
In this activity, we examine notions of counting.

      
\end{abstract}
      
\maketitle
 
\begin{problem}
Suppose that an inspector needed to visit 5 factories in one week, how many different ways could she choose to visit these factories in order? $\answer{120}$
\end{problem}

\begin{problem}
If a teacher has a class of 25 and needs to pick 5 students to present homework, how many ways could she do this? $\answer{53130}$
\end{problem}

\begin{problem}
A professor assigns 10 problems and a student chooses to do 5.  The professor then selects 5 problem at random to grade.

\begin{enumerate}
\item What is the probability that the teacher grades the same 5 problems the student did?  $\answer{1/252}$.
\item What is the probability that the teacher grades 3 out of the  5 problems the student did?  $\answer{100/252}$.
\end{enumerate}

\end{problem}

\begin{problem}
A farmer has 3 types of barely seeds, 4 oats, 5 corn.  Suppose the farmer can only plant 4 crops.

\begin{enumerate}
\item How many ways can he plant crops if he uses all 3 strands of barley? $\answer{9}$
\item What is the probability that if he randomly picks his crops, he uses all 3 strands of barley? $\answer{9/495}$
\end{enumerate}


\end{problem}

\begin{problem}
A  science department has 4 mathematicians, 4 chemists and 4 biologists.  A committee of 5 must be selected.

\begin{enumerate}
\item How many ways to select a committee with no mathematicians? $\answer{56}$
\item What is the probability that if a committee is selected at random that there is at least 1 mathematician? $\answer{736/792}$
\end{enumerate}


\end{problem}



\end{document}
