\documentclass{ximera}
      
\title{Counting}
      
\begin{document}
      
\begin{abstract}
      
In this activity, we examine notions of counting as related to probabilities.

      
\end{abstract}
      
\maketitle
 

\begin{problem}
A professor assigns 15 problems and a student chooses to do 5.  The professor then selects 5 problem at random to grade.

\begin{enumerate}
\item What is the probability that the teacher grades the same 5 problems the student did?  $\answer{1/3003}$.
\item What is the probability that the teacher grades 3 out of the  5 problems the student did?  $\answer{450/3003}$.
\end{enumerate}

\end{problem}

\begin{problem}
A farmer has 3 types of barely seeds, 4 oats, 5 corn.  Suppose the farmer can only plant 4 crops.

\begin{enumerate}
\item How many ways can he plant crops if he uses  3 strains of oats? $\answer{32}$
\item What is the probability that if he randomly picks his crops, he uses  3 strains of corn? $\answer{32/495}$
\end{enumerate}


\end{problem}

\begin{problem}
A  science department has 6 mathematicians, 5 chemists and 4 biologists.  A committee of 5 must be selected.

\begin{enumerate}
\item How many ways to select a committee with no mathematicians? $\answer{126}$
\item What is the probability that if a committee is selected at random that there is at least 1 mathematician? $\answer{2877/3003}$
\end{enumerate}


\end{problem}


\begin{problem}
Suppose the CDC stops a bus with 30 people on it, and 10 of them are infected with a virus.  The CDC tests 6 subjects randomly.
\begin{enumerate}
\item What is the probability that none of the tested subjects are infected? $\answer{38760/593775}$
\item What is the probability that half the tested subjects are infected? $\answer{136800/593775}$
\end{enumerate}

\end{problem}


\begin{problem}
In a class of 24 students, 10 did the homework.  If 3 students are asked to present the homework, what is the probability that at least two of them will have done the homework? $\answer{1030/2024}$
\end{problem}

\end{document}
