\documentclass{ximera}
      
\title{Probability}
      
\begin{document}
      
\begin{abstract}
      
In this activity, we examine notions of probability.

Problems are based on the material found in section 3.2 \url{https://cnx.org/contents/MBiUQmmY@18.50:0_rgGM3Y@4/Two-Basic-Rules-of-Probability}
      
\end{abstract}
      
\maketitle
 
\begin{problem}
Suppose that there is an 80\% chance that today I will either eat breakfast or lunch.  There is a 60\% chance I eat breakfast and 40\% chance I eat lunch.  If I eat breakfast, what is the probability I eat lunch?  $\answer{1/3}$
\end{problem}

\begin{problem}
Suppose that 70\% of graduate students in Humanities disciplines complete their degree and 55\% of STEM graduate students do.  If 60\% of a graduate school is Humanities and 40\% STEM, how many will graduate?  $\answer{0.64}$
\end{problem}

\begin{problem}
A drug test has a 95\% chance of correctly identifying that a person uses drugs, but also has a 10\% chance of falsely identifying someone who doesn't use drugs as a drug user.  If 80\%of a companies employees are identified by the test as drug users, how many actually used drugs? (round to four places if necessary) $\answer{0.8235}$
\end{problem}


\begin{problem}
Suppose that at a restaurant, 20\% of the customers ordered chicken, 10\% got sick, and 20\% of the people who ordered chicken got sick.  How many people either ordered chicken or got sick? $\answer{0.26}$
\end{problem}

\begin{problem}
Suppose that at a restaurant, 20\% of the customers ordered chicken, 10\% got sick, and 20\% of the people who ordered chicken got sick.  If you got sick, what was the probability you ordered chicken? (round to 4 places if neccesary) $\answer{0.1538}$
\end{problem}


\end{document}
